Paper 1: Vitis

### 2018-02-21 Paper-1-Vitis.Rmd
Commit from RStudio

```{r}
ac_tba_glm <- glm(leaf~teeth.blade.area, data = ac_all, family = gaussian())
summary(ac_tba_glm)
plot(ac_tba_glm)
beep(sound = 3, expr = NULL)
```

We ran a GLM for leaf number and multiple variables. 
```{r}
ac_clim_glm <- glm(leaf~feret.diameter.ratio + tooth.area.blade.area + teeth.blade.area + teeth.int.perimeter, data = ac_all, family = gaussian())
summary(ac_clim_glm)
plot(ac_clim_glm)
```

>>>>

```{r}
ac_tba_glm <- glm(leaf~teeth.blade.area, data = ac_all, family = gaussian())
summary(ac_tba_glm)
plot(ac_tba_glm)
```

We ran a GLM for leaf number and multiple variables. 
```{r}
ac_clim_glm <- glm(leaf~feret.diameter.ratio + tooth.area.blade.area + teeth.blade.area + teeth.int.perimeter, data = ac_all, family = gaussian())
summary(ac_clim_glm)
plot(ac_clim_glm)
beep(sound = 3, expr = NULL)
```
